%%% A %%%
\subsection{External Interface Requirements}

	\subsubsection{User Interfaces}				
		\input{Subsections/section3/userInterfaces.tex}
	
	\subsubsection{Hardware Interfaces}
		The system allows to interact with all the possible processors that are in the devices of the two companies Android and Apple. Among the most important processors there are: Qualcomm, ARM and Exynos.

	\subsubsection{Software Interfaces}
		\hfill		
		\begin{enumerate}
			\item Android
				\begin{itemize}
					\item[-] Name: Lollipop
					\item[-] Version: 5.0+
					\item[-] Source: \url{https://www.android.com/intl/it_it/versions/lollipop-5-0/}
				\end{itemize}
								
			\item Apple
				\begin{itemize}
					\item[-] Name: iOS
					\item[-] Version: 8.0+
					\item[-] Source: \url{https://www.apple.com}
				\end{itemize}
								
			\item Google Maps APIs
				\begin{itemize}
					\item[-] Name: Google Maps APIs
					\item[-] Source: \url{https://developers.google.com/maps/}
				\end{itemize}
		\end{enumerate}
			
	\subsubsection{Communication Interfaces}
		The system also interface with the applications for the use of sharing and payment services
		\hfill
		\begin{tabular}{| c | c | c |}
			\hline
			Protocol	& Application	& Port \\
			\hline
			\hline
			TCP		& HTTP		& 443 \\
			\hline
			TCP		& HTTP		& 80 \\
			\hline
		\end{tabular}
	
%%% B %%%						
\subsection{Functional Requirements}
	\input{Subsections/section3/requirements.tex}
	
	\subsubsection{Use Case Diagrams}
		\input{Subsections/section3/useCase.tex}

	\subsubsection{Sequence Diagrams}
		\input{Subsections/section3/sequenceDiagrams.tex}		
			
%%% C %%%
\subsection{Performance Requirements}
This section is useful to see how the application manages statical and dynamical non-functional requirements in terms of quantity and quality. 
	In particular:
	\begin{description}
		\item[Static Non-Functional Requirements]	\vfill
		\hfill
		\begin{enumerate}
			\item Application it was developed to handle until 50.000 users simultaneously.
			\item Mobile application must run on two most importante operative system: iOS and Android.
		\end{enumerate}
		
		\item[Dynamic Non-Functional Requirements] \vfill
		\hfill
		\begin{enumerate}
			\item 98\% of the requestes shall be processed in less than 2 second.
			\item The system should be able 99.8\% of the time in one year.
		\end{enumerate}			

	\end{description}
		
		
%%% D %%%	
\subsection{Design Constraints}
		\begin{description}
			\item[Standards compliance]
			The system must require User’s location to work, so the application asks for it according to privacy laws the first time the user runs the application.
			The payment system is guaranteed by the corresponding external application, so \textit{Travlendar+} doesn’t ask users for their credit card number.

			\item[Hardware limitations]
			Mobile app:
			\begin{itemize}
			\item Space for app package
			\item 3G connection or better
			\item GPS
		\end{itemize}

			\item[Any other constraint]
			No further constraints are imposed
\end{description}
		
%%% E %%%		
\subsection{Software System Attributes}
	\input{Subsections/section3/softwareSystemAttributes.tex}
